White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2016-07-17 papers/wdmerger_II/paper.tex
Update the impact parameter plot

As the impact parameter varies for a head-on collision, the cross-section of the contact
zone between the two stars varies in size and geometry. In \autoref{fig:impact_parameter}, we
see the dependence of the nickel production on the impact parameter $b$, measured in units
of the WD radius. This test was performed using the 3D setup at our usual base resolution of
400 km. For computational efficiency, timestep limiting based on burning was disabled.
We sampled at $b = 0.0$, $0.01$, $0.02$, $0.03$, $0.04$, $0.05$, and then increasing
in increments of $0.05$. There is no clear pattern in the data, with the nickel production varying
significantly even for small changes in the impact parameter. The typical value is around $0.15\ \msolar$.
It is worth nothing that for $b = 0.0$ the nickel production is a bit smaller for the 3D simulation
than its equivalent 2D simulation, the default case described above.

>>>>

As the impact parameter varies for a head-on collision, the cross-section of the contact
zone between the two stars varies in size and geometry. In \autoref{fig:impact_parameter}, we
see the dependence of the nickel production on the impact parameter $b$, measured in units
of the WD radius. This test was performed using the 3D setup at our usual base resolution of
400 km. For computational efficiency, timestep limiting based on burning was disabled.
We sampled at $b = 0.0$, $0.01$, $0.02$, $0.03$, $0.04$, $0.05$, and then increasing
in increments of $0.05$. Relative to $b = 0$, there is a slight increase in nickel production for small
but non-zero $b$, which then declines with increasing $b$ except for a bump at $b = 0.5$.
For $b \ge 0.7$, no detonation forms at all, and the merged object remains a stable C/O WD
with $M = 1.2\ \msolar$ at least until $t = 100$.

It is worth nothing that for $b = 0.0$ the nickel production is a bit smaller for the 3D simulation
than its equivalent 2D simulation, the default case described above. There are differences both in
the size of the timestep (which as we saw in \autoref{sec:parameters:timestepping} plays a role in
the total nickel production) and in the discretized nature of the stars; the assumption of perfect
azimuthal symmetry inherent to the 2D simulation breaks down for the 3D simulation, especially at
low resolution, since the zones are rectangular.
